Weak lensing Hierarchy Bayesian Inference

### 2013-02-13 write-up.tex
a

$\ \ \ \ $Weak Lensing has become one of the most powerful method
in exploring the dark universe (Al- brecht et al. 2006; Peacock \&
Schneider 2006 )

As dark energy slows the growth of dark matter structures, these in
turn affect the appearance of distant galaxies, distorting them slightly
as gravitational fields deflect their light. This distortion is known
as cosmic shear.()

The measurement of cosmic shear is determined by the amount of distortion
caused to a forewground galaxy. Due to the isotropic universe the
expect value of a galaxy's intrinsic complex ellipticity is 0. Therefore
the comples ellipticity of a stretched galaxies is an unbiased estimation
of cosmic shear.However, the distortion induced by cosmic shear is
typically on the order of a few percent,which is significantly smaller
than the galaxies's intrinsic shape noise(\textasciitilde{}0.1 level).

@@

\end{verse}
Then we make N random samples from a selected distribution as the "true" reduced shear on each patch.

Finally we calculated the sheared shape of every galaxy on each patch.

@@

One intresting thing in shear survey is that the assumption that galaxy
pairs have no ellipticity correlation is not entirely accurate. There
are intrinsic alignments of nearby galaxies due to the alignment of
angular momentum produced by tidal shear correlations( Heymans C.,
Brown M., Heavens A., Meisenheimer K., Taylor A., Wolf C., 2004, MNRAS,
347, 895 ;B. Casaponsa, A. F. Heavens, T. D. Kitching, arxive,2013).Consider
the ellipticity the first assumption of traditional average method
$<\epsilon_{0}>=0$ does not stands any more,while for this Hierarchy
Bayesian method though we are also using the assumption that intrinsic
orientational angle distribution is a flat distribution, we can just
re-model it once more information on galaxy shape coorelation is uncovered.
\end{document}

>>>>

$\ \ \ \ $Weak Lensing has become one of the most powerful method
in exploring the distribution of matter in the Universe on large scales
(Bartelmann \& Schneider 2001,Al- brecht et al. 2006; Peacock \& Schneider
2006 ).This powerful method has a various astronomical applications.By
detecting the weak lensing shear or magnification effect we are able
to reconstruct the mass properties of galaxy clusters,as well as dark
matter halos(Dahle et al. 2002; Gray et al. 2002; Clowe, Gonzalez
\& Markevitch 2004;Sheldon et al. 2004)

General relativity predicts that the path of light from a distant
galaxy is distorted by the gravitational potential fluctu- ations
along the line of sight. As dark energy slows the growth of dark matter
structures, these in turn affect the appearance of distant galaxies,
distorting them slightly as gravitational fields deflect their light.
This distortion is known as cosmic shear.()

The measurement of cosmic shear is determined by the amount of distortion
caused to a forewground galaxy. Due to the isotropic universe the
expect value of a galaxy's intrinsic complex ellipticity is 0. Therefore
the comples ellipticity of a stretched galaxies is an unbiased estimation
of cosmic shear(Bartelmann \& Schneider 2001).However, the distortion
induced by cosmic shear is typically on the order of a few percent,which
is significantly smaller than the galaxies's intrinsic shape noise(\textasciitilde{}0.1
level).

@@

\end{verse}
Then we make N samples from the prior distriibution of g.In this paper
we assume the prior distribution of g is gaussian with $\sigma=0.1$.

Finally galaxies in N patches are sheared by N different gamma .

@@

One intresting in shear survey is that the assumption that galaxy
pairs have no ellipticity correlation is not entirely accurate. There
are intrinsic alignments of nearby galaxies due to the alignment of
angular momentum produced by tidal shear correlations( Heymans C.,
Brown M., Heavens A., Meisenheimer K., Taylor A., Wolf C., 2004, MNRAS,
347, 895 ;B. Casaponsa, A. F. Heavens, T. D. Kitching, arxive,2013).Consider
the ellipticity the first assumption of traditional average method
$<\epsilon_{0}>=0$ does not stands any more,while for this Hierarchy
Bayesian method though we are also using the assumption that intrinsic
orientational angle distribution is a flat distribution, we can just
re-model it once more information on galaxy shape coorelation is uncovered.
\end{document}
